Rank Verification for Exponential Families

### 2017-08-28 poster.tex
minor fixes, new keywords added

\begin{itemize}
	\item {\em Multiple comparison}: Null hypothesis is ``the winner is not the best'', a union null of hypothesis that the winner is not better than each of the rest
	\item Construct a $p$-value $p_{ij}$ for comparing winner $i$ to each of the rest, $j$; do a significance test based on the combined $p$-value $\max_{j \ne i} p_{ij}$.
	\item {\em Selective inference}: Construct $p_{ij}$ by conditioning on the selection event \citep{Fithian:2014ws}, given by
	\[
	\{X_i > \max_{i \ne k} X_k\}
	\]
	\item Condition also on sufficient statistics for nuisance parameters, $X_{\setminus\{i, j\}}$ and $X_i + X_j$, for an exact test
\end{itemize}

@@

\begin{block}{Brief Sketch for Other Two Inferences}

@@

\centering
\includegraphics[width=\textwidth]{multinomial-power.pdf}

>>>>

\begin{itemize}
	\item {\em Multiple comparison}: Null hypothesis is ``the winner is not the best'', a union of null hypotheses, each stating that the winner is not better than one other candidate
	\item Construct a $p$-value $p_{ij}$ for comparing winner $i$ to each of the rest, $j$; do a significance test based on the combined $p$-value $\max_{j \ne i} p_{ij}$.
	\item {\em Selective inference}: Construct $p_{ij}$ by conditioning on the selection event \citep{Fithian:2014ws}, given by
	\[
	\{X_i > \max_{i \ne k} X_k\}
	\]
	\item Condition also on sufficient statistics for nuisance parameters, $X_{\setminus\{i, j\}}$ and $X_i + X_j$, for an exact test
\end{itemize}

@@

\begin{block}{Proof Sketch for Other Two Procedures}

@@

\centering
\includegraphics[width=\textwidth]{multinomial-power.eps}
